background points - is more better?

### 2019-01-08 src/background_points_no_check.Rmd
updated to use new background point list

load one of the raw background.csv files to randomly extract points from (note that these files do not include presence cells, but will do for this test)

```{r}
testbglist <- read.csv("../output/bio/background/raw/2006.2.csv", header = TRUE)
head(testbglist)
```

Now create a bunch of dataframes with different no of random cells selected

SAM - A BETTER WAY WOULD HAVE BEEN TO RUN THE LOOP ON ALL THE POINTS, THEN RANDOMLY SELECT (QUICKER)

```{r}
testbk10000 <- testbglist[sample(nrow(testbglist), 10000), ]  #where 10000 = number of rows to sample (large sample as per maxent)
testbk20000 <- testbglist[sample(nrow(testbglist), 20000), ]  
testbk30000 <- testbglist[sample(nrow(testbglist), 30000), ]  
testbk50000 <- testbglist[sample(nrow(testbglist), 50000), ]  
testbk100000 <- testbglist[sample(nrow(testbglist), 100000), ]  
testbk190000 <- testbglist[sample(nrow(testbglist), 190000), ]  
```

# this test will use a shorter dataset and a smaller number of netcdfs
# the inefficent loop

@@

@@

xy <- testbk190000[ ,c("longitude_","latitude_m")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
testbk190000sp <- SpatialPointsDataFrame(coords = xy, data = testbk190000, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.

@@

    }
}
write.csv(testbk190000sp, "../data/testbk190000output.csv", row.names = FALSE)
#test_back_df <- as.data.frame(testbk100000sp)
#head(test_back_df)
print(Sys.time()-strt) #time it took to run
```

plot each variable against the different no of backgrounn points

```{r}
test10000 <- as.data.frame(testbk10000sp)
test20000 <- as.data.frame(testbk20000sp)
test50000 <- as.data.frame(testbk50000sp)
test100000 <- as.data.frame(testbk10000sp)
test190000 <- as.data.frame(testbk190000sp)
```

```{r}
ggplot(test10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/ssh_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/mlp_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/chl_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/chl_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/o2_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/o2_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/1999_02/testbglistoutput.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
#head(test_back_df)
print(Sys.time()-strt) #time it took to run
```

@@

```{r}
ggplot(testbk100001999, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/ssh_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/mlp_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_surface_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_depth_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_surface_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_depth_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/chl_surface_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/chl_depth_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/o2_surface_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/o2_depth_back_no_1999.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/2014_06/testbglistoutput.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
#head(test_back_df)
print(Sys.time()-strt) #time it took to run
```
ok now create the first lot of random for 2014_06

@@

```{r}
ggplot(testbk100002014, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/ssh_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/mlp_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_surface_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/temp_depth_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_surface_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/salinity_depth_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../data/chl_surface_back_no_2014.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

>>>>

load the raw background.csv file with all points to randomly extract points from (../output/env/unique_cell_centroid_lonlat_nafo2_depth.csv)

```{r}
testbglist <- read.csv("../output/env/unique_cell_centroid_lonlat_nafo2_depth.csv", header = TRUE)
head(testbglist)
```

```{r}
backobsno <- nrow(testbglist)
backobsno
```

# the inefficent loop

@@

Start with 2007_10 data

@@

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/200710_allbackgroundpoints.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
print(Sys.time()-strt) #time it took to run
```

ok now create the first lot of random for 2007_10

plot each variable against the different no of background points

```{r}
ggplot(test10000, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_ssh_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_mlp_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_temp_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_salinity_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_chl_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_surface_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(test10000, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=test20000 , na.rm = TRUE, colour = "blue") + geom_density(data=test50000 , na.rm = TRUE, colour = "green") + geom_density(data=test100000 , na.rm = TRUE, colour = "orange") + geom_density(data=test190000 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/200710_o2_depth_back_no.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/199902_allbackgroundpoints.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
print(Sys.time()-strt) #time it took to run
```

@@

```{r}
ggplot(testbk100001999, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_ssh_back.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_chl_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_o2_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100001999, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200001999 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500001999 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000001999 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900001999 , na.rm = TRUE, colour = "pink")
dev.copy(png,".../output/env/background_point_check/199902_o2_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

    }
}
write.csv(testbglistsp, "../data/env/background_point_check/201406_allbackgroundpoints.csv", row.names = FALSE)
test_back_df <- as.data.frame(testbglistsp)
print(Sys.time()-strt) #time it took to run
```
ok now create the first lot of random for 2014_06

@@

```{r}
ggplot(testbk100002014, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_ssh.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_mlp.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_temp_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_salinity_depth.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png

ggplot(testbk100002014, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=testbk200002014 , na.rm = TRUE, colour = "blue") + geom_density(data=testbk500002014 , na.rm = TRUE, colour = "green") + geom_density(data=testbk1000002014 , na.rm = TRUE, colour = "orange") + geom_density(data=testbk1900002014 , na.rm = TRUE, colour = "pink")
dev.copy(png,"../output/env/background_point_check/201406_chl_surface.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
